A Sample Document

### 2017-04-06 Writing/rsptime.tex
Added a 114 words story to fingerprint...

\subsection{Program Fingerprint}
%Fingerprints the code running on a device, which leads to plaintext recovery.
%\begin{itemize}
%	\item Theory explained in \Cref{FingerprintTheory}.
%	\item Requirement: needs to actively send messages. Any Request/Response protocol works, such as PING, DTLS Heartbeat, CoAP PING, etc. 
%	\item Not for 802.15.4: adversary can't join the network.
%	\item For DTLS: PING is available and confirmed. DTLS Heartbeat should work if supported.
%\end{itemize}
The response time of packets could also be exploited to fingerprint the code running on a specific device.

>>>>

\subsection{Program Fingerprint}
%Fingerprints the code running on a device, which leads to plaintext recovery.
%\begin{itemize}
%	\item Theory explained in \Cref{FingerprintTheory}.
%	\item Requirement: needs to actively send messages. Any Request/Response protocol works, such as PING, DTLS Heartbeat, CoAP PING, etc. 
%	\item Not for 802.15.4: adversary can't join the network.
%	\item For DTLS: PING is available and confirmed. DTLS Heartbeat should work if supported.
%\end{itemize}
The program executing on the target is a valuable information in aspect of security and privacy, as it determines functionality of a device and therefore the contents of encrypted packets associated. For instance, knowing a target being an actuator that controls an air conditioner immediately suggests a packet directed to it might  be a controlling command.

Our study shows that the response time of packets could also be exploited to reveal information of the program target is executing. To be more specifically, an adversary can collect ``fingerprints'', which we explain in the following section, from products available on the market and then use this information to breach the program running on a target device.
